Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Redraw skipper 5 picture

\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{coffee2}

@@

@@

\begin{figure}[tb]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
\caption{A pictorial representation of a skipper (skipper 5) with multicoloured
state and grey timeslots. The schedule for skipper 5 is in bold and the
deterministic finite automata for criteria 4, 11 and 12 is drawn with state
$\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
in pink and $\END$ in red.}
\label{skipper5}
\end{figure}

>>>>

\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{tikz}
\usepackage{coffee2}

\usetikzlibrary{shapes, shapes.multipart, arrows, positioning}

@@

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}

\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

@@

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}
    \begin{scope}[every node/.style={minimum size=2em,inner sep=1}, xshift=-1cm]
        \node (DFAS) [draw, circle, fill=white]                     at (0,  0)   { \textsc{S} };
        \node (DFAF) [draw, circle, fill=uofgcobalt]                at (2,  1.7) { \textsc{F} };
        \node (DFAM) [draw, circle, fill=uofgsunshine]              at (2,  0)   { \textsc{M} };
        \node (DFAL) [draw, circle, fill=uofglawn]                  at (2, -1.7) { \textsc{L} };
        \node (DFAB) [draw, circle, fill=uofgthistle, text=white]   at (4,  0)   { \textsc{B} };
        \node (DFAE) [draw, circle, fill=uofgpillarbox, text=white] at (6,  0)   { \textsc{E} };

        \draw [->, >=latex, thick] (DFAS) to (DFAF);
        \draw [->, >=latex, thick] (DFAS) to (DFAM);
        \draw [->, >=latex, thick] (DFAS) to (DFAL);
        \draw [->, >=latex, thick] (DFAS) to [out=-25, in=-155] (DFAB);

        \draw [->, >=latex, thick] (DFAF) to [out=60, in=120, looseness=6] (DFAF);
        \draw [->, >=latex, thick] (DFAF) to [out=-125, in=125] (DFAL);
        \draw [->, >=latex, thick] (DFAF) to (DFAB);
        \draw [->, >=latex, thick] (DFAF) to [out=0, in=135] (DFAE);

        \draw [<->, >=latex, thick] (DFAF) to (DFAM);

        \draw [->, >=latex, thick] (DFAM) to [out=60, in=120, looseness=6] (DFAM);
        \draw [->, >=latex, thick] (DFAM) to [out=-25, in=-155] (DFAE);

        \draw [<->, >=latex, thick] (DFAM) to (DFAB);
        \draw [<->, >=latex, thick] (DFAM) to (DFAL);

        \draw [->, >=latex, thick] (DFAL) to [out=300, in=240, looseness=6] (DFAL);
        \draw [->, >=latex, thick] (DFAL) to [out=0, in=225] (DFAE);

        \draw [<->, >=latex, thick] (DFAL) to (DFAB);

        \draw [->, >=latex, thick] (DFAB) to [out=30, in=-30, looseness=6] (DFAB);

        \draw [->, >=latex, thick] (DFAE) to [out=30, in=-30, looseness=6] (DFAE);
    \end{scope}

    \begin{scope}[yshift=5.5cm, scale=0.85]
        \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofglawn,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofglawn,uofgpillarbox}] at (0, 0) {
            \nodepart[text width=2em, align=center] {one}   \textsc{L}
            \nodepart[text width=2em, align=center] {two}   \textsc{L}
            \nodepart[text width=2em, align=center] {three} \textsc{M}
            \nodepart[text width=2em, align=center] {four}  \textsc{F}
            \nodepart[text width=2em, align=center] {five}  \textsc{F}
            \nodepart[text width=2em, align=center] {six}   \textsc{L}
            \nodepart[text width=2em, align=center, text=white] {seven} \textsc{E}
        };

        \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
            \nodepart[text width=0.75em, align=center] {one}
            \nodepart[text width=0.75em, align=center] {two}
            \nodepart[text width=0.75em, align=center] {three} 4
        };

        \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
            \nodepart[text width=0.75em, align=center] {one}
            \nodepart[text width=0.75em, align=center] {two}
            \nodepart[text width=0.75em, align=center] {three} 1
        };

        \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
            \nodepart[text width=0.75em, align=center] {one}
            \nodepart[text width=0.75em, align=center] {two} 0
            \nodepart[text width=0.75em, align=center] {three}
        };

        \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
            \nodepart[text width=0.75em, align=center] {one} 6
            \nodepart[text width=0.75em, align=center] {two}
            \nodepart[text width=0.75em, align=center] {three}
        };

        \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
            \nodepart[text width=0.75em, align=center] {one} 3
            \nodepart[text width=0.75em, align=center] {two}
            \nodepart[text width=0.75em, align=center] {three}
        };

        \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
            \nodepart[text width=0.75em, align=center] {one}
            \nodepart[text width=0.75em, align=center] {two}
            \nodepart[text width=0.75em, align=center] {three} 2
        };

        \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
            \nodepart[text width=0.75em, align=center] {one} \phantom{1}
            \nodepart[text width=0.75em, align=center] {two}
            \nodepart[text width=0.75em, align=center] {three}
        };

        \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
        \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
        \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
        \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
        \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
        \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
        \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
    \end{scope}

    \begin{scope}
        \node at (-3.8, 0) {
            \begin{minipage}{4cm}
            \begin{framed}
                \centering
                \begin{tabular}{c@{\hspace{3mm}}c@{\hspace{3mm}}c}
                    (0, 1) & (2, 3) & \textbf{(4, 5)} \\
                    (0, 2) & (4, 6) & \textbf{(1, 5)} \\
                    (2, 6) & \textbf{(0, 5)} & (1, 3) \\
                    \textbf{(5, 6)} & (0, 3) & (1, 4) \\
                    \textbf{(3, 5)} & (1, 6) & (2, 4) \\
                    (3, 6) & (0, 4) & \textbf{(2, 5)} \\
                    (3, 4) & (1, 2) & (0, 6) \\
                \end{tabular}
            \end{framed}
            \end{minipage}
        };
    \end{scope}

    \end{tikzpicture}
    \caption{A pictorial representation of a skipper (skipper 5) with multicoloured
        state and grey timeslots. The schedule for skipper 5 is in bold and the
        deterministic finite automata for criteria 4, 11 and 12 is drawn with state
        $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
    in pink and $\END$ in red.}\label{skipper5}
\end{figure}
